### 2020-11-02 Thesis-Chapter4-Arguments.tex
Create going dark and golden age arg maps

>>>>

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too much} or \ii{too little} access to data.

See the ``Going Dark'' argument in \myfig{fig-arg-going-dark}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.goingdark.pdf}
  \caption{A ``Going Dark'' Argument Map}
  \label{fig-arg-going-dark}
\end{figure}

See the ``Golden Age of Surveillance'' argument in \myfig{fig-arg-golden-age}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.goldenage.pdf}
  \caption{A ``Golden Age of Surveillance'' Argument Map}
  \label{fig-arg-golden-age}
\end{figure}
